\documentclass[a4paper,12pt]{article}




% Paweł Antoniuk \\ Email: pawel.antoniuk@sd.pb.edu.pl \\ Faculty of Computer Science \\ Białystok University of Science \\ Wiejska 45A, 15-351 Białystok \\ Poland
% \signature{Paweł Antoniuk}

\begin{document}

% \begin{tabular}{l @{}}
%     \hfill \today \bigskip                         \\ % Date
%     \hfill XXX                                     \\
%     \hfill Email: xxx@mail.ynu.edu.cn              \\
%     \hfill 2 Cuihu North Road, Wuhua District,     \\
%     \hfill Kunming, Yunnan Province, 650504, China \\ % Address
% \end{tabular}

% # Speech processing and communication systems

Dear Editor,

We are submitting a manuscript for prospective publication in Archives of Acoustics. The title of the paper is ``Estimating Ensemble Location and Width in Binaural Recordings of Music with Convolutional Neural Networks''. The manuscript is authored by Paweł Antoniuk (corresponding author) and Sławomir Krzysztof Zieliński.
\begin{itemize}
    \item We are submitting the paper to Archives of Acoustics as we believe its content fits well within the scope of the journal (the area of speech processing and communication systems).
    \item ‘Speech processing and communication systems’ constitute the field of acoustics covered by Archives of Acoustics, according to the journal website.
    \item We affirm that this manuscript has not been published elsewhere and is not under consideration by another journal.
    \item We suggest the following reviewers:
          \begin{itemize}
              \item 3 pierwszych z cover letter Antoniny
            %   \item Flip jackson profesor
          \end{itemize}
    \item In our opinion the manuscript should be classified as a ``research paper,'' considering the empirical content of the study described.
    \item We are aware that the manuscript exceeds the recommended 20-page limit. This has been caused by the need to describe the methodology at sufficient level of detail, allowing other researchers to replicate our study. Therefore, we believe that the extended content is in this case justified.
\end{itemize}

Thank you in advance for considering the manuscript.

\end{document}


% 1. tabela: signal to noise rate, MAE, korelacja, szum tyko zbior testowy, pink noise, bez modulacji, dla 10 itracji z std dev, np. 7, w db
% 2. prztestowanie modelu dla warunkow echowych